---
title: "Exploring Variations in Sleep Duration Across Occupations"
author: "Justin Naidu"
date: "`r Sys.Date()`"
output: html_document
params:
  production: TRUE
---

```{r, set-chunk-opts, echo = FALSE, eval = params$production}

library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)

```


```{r, load-data}

here::i_am("sleep_report.Rmd")
data <- readRDS(
  file = here::here("output/data_clean.rds")
)

```


# Introduction
The data set examined in this final project report is the "Sleep, Health, and Lifestyle" data set. This data set was created by Henry Shan and is accessible through the Kaggle website.

#### Data Set Description
The data set contains a wide range of variables related to sleep and daily routines. The data set includes variables such as gender, age, occupation, sleep duration, sleep quality, physical activity, stress level, BMI, blood pressure, heart rate, daily steps taken, and presence of sleep disorders. 

#### Primary Objective
The primary objective of my analysis are: 

1. Investigate the influence of different professions on the variability in sleep duration by computing the averages in tabular format.
2. Generate scatterplots to visually represent the trends in variability of sleep duration across different occupations.

# Descriptive Analysis

### Tabular Analysis
This table provides a summary of key characteristics related to sleep health and lifestyle. Variables include gender, age, occupation, duration of sleep, and quality of sleep. Counts and percentages for categorical variables, as well as mean (SD) for continuous variables, are presented.

```{r, table1}

table_one <- readRDS(
  file = here::here("output/table_one.rds")
)
table_one

```


### Graphical Analysis

The bar chart illustrates the average sleep duration across different occupations. Notably, engineers exhibit a significantly higher bar, indicating a greater average sleep duration (7.9). In contrast, sales representatives have the lowest bar, suggesting a shorter average sleep duration (5.9).

```{r, plot-data}

#| fig.align = "center",
#| out.width = "475px"
knitr::include_graphics(
  here::here("output/scatterplot.png")
)

```
